Clicks and Cliques

### 2018-12-19 papersoul.Rnw
tidy code for cluster.cen parallel plot

\begin{figure}[hbpt]
<<cluster.cen, dependson=c('data','corplot'), echo=FALSE,message=FALSE,warning=FALSE>>=
# var.cl2 <- colnames(census.data) %in% c("aveageF","prop1821", "Bachelor.s.degree.or.higher." , "gini" , "own.rate" , "afri.prop",'prop.new.entry','un.rate',"prop.no.workers" )
d2 <- census.data %>% select(aveageF, prop1821, Bachelor.s.degree.or.higher., gini , own.rate , afri.prop, prop.new.entry, un.rate, prop.no.workers ) %>% dist()

# d2 <- dist(census.data[, var.cl2])
hc2 <- hclust(d2, method = 'ward.D')
# census.data$cl.2 <- cutree(hc2, 4)

# Characterize the clusters with the numerical variables
nn <- c('cl.2', 'Age.Fem', '1821.Yr','Bachelor', 'Unemp','Gini','Own.rate', 'Afri.pr', 'No.workers', 'New.entry' )

census.data %>%
  mutate(cl.2 = cutree(hc2, 4) ) %>% 
  select( c(colnames(census.data)[var.cl2],'cl.2' ) ) %>% 
  group_by(cl.2) %>%
  summarise_all(funs(mean)) %>%
  setNames(nn) %>% ungroup() %>%
  mutate(cl.2 = factor(cl.2)) %>% 
  ggparcoord(columns = 2:10, scale = 'std', 
             groupColumn = 'cl.2', showPoints = T, 
             order = c(4, 10, 2, 7, 8, 6, 3,5, 9))  + 
  theme(axis.text.x = element_text(angle = 90, size = I(15))) + 
  labs(x = '', y = '') + 
  scale_color_brewer(type = 'qual', palette = 2, name = 'Group')

  # c(3, 4, 6, 10, 2, 5, 9, 7, 8)
@
\caption{Parallel coordinate plot for community cluster means. \label{cluster.cen} }
\end{figure}

>>>>

\begin{figure}[hbpt]
<<cluster.cen, dependson=c('data','corplot'), echo=FALSE,message=FALSE,warning=FALSE>>=

d2 <- census.data %>% 
  select(aveageF, prop1821, Bachelor.s.degree.or.higher., gini , own.rate , afri.pro, prop.new.entry, un.rate, prop.no.workers ) %>%
  dist()

hc2 <- hclust(d2, method = 'ward.D')

census.data %>%
   mutate(cl.2 = cutree(hc2, 4) ) %>%
     select(aveageF, prop1821, un.rate, Bachelor.s.degree.or.higher., gini , own.rate ,  prop.new.entry, afri.prop, prop.no.workers, cl.2) %>% 
  group_by(cl.2) %>%
  summarise_all(funs(mean)) %>%
  ungroup() %>%
  rename(Age.Fem = aveageF, Yr.1821 = prop1821, Unemp = un.rate, Bachelor = Bachelor.s.degree.or.higher., Gini = gini, Own.rate = own.rate, New.entry = prop.new.entry, Afri.pr= afri.prop, No.workers = prop.no.workers, cl.2 = cl.2) %>% 
  mutate(cl.2 = factor(cl.2)) %>%
  ggparcoord(columns = 2:10, scale = 'std',
             groupColumn = 'cl.2', showPoints = T, 
             order = c(3, 5, 6, 8, 2, 4, 10, 7, 9))  + 
  theme(axis.text.x = element_text(angle = 90, size = I(15))) + 
  labs(x = '', y = '') + 
  scale_color_brewer(type = 'qual', palette = 2, name = 'Group')

@
\caption{Parallel coordinate plot for community cluster means. \label{cluster.cen} }
\end{figure}
